A thesis draft

### 2018-10-19 res/sections/08-Background.tex
Add new file, add content in background section

\subsubsection{Network slicing}
The role of a ``network slice'' in a 5G architecture is to specificatly handle a
Control-place of a praticular service (e.g. smartphones traffic, autonomous
driving, massive IoT), deploying resources in a manner that assure the required
latency, security and reliability. While some very peculiar legacy services
could require specific hardware, the common resources between services could be
shared in a virtualized way, providing auto-scaling capabilities in services
that are under heavy network pressure.

@@

The analysis of this topic revealed to be trivial: since internet has many
different protocols that would become infeasible to support all of them at the
same time, packet incapsulation present itself as the only faseable solution:
every packet incoming in the VNFs has already been encapsulated by the MANO,
\todo{Not sure about this, please give it a check - Not sure but I think that it
  is not part of the MANO the encapsulation of the packets. Also I think that
  the main purpose of UDP encapsulation is not to hide the protocol used on the
  edges but 1) usa a ``quick protocol to exchange data among VNFs and 2) we are
  hiding the path not the protocol itself. As we were discussing, we are
  creating some sort of proxy, so the aim will be the same even if we support a
  plethora of protocols.''} making the whole architecture indipendent from the
protocol a particolar flux of data uses. To achieve this, TUN/TAP interfaces 
were used to deploy a tunnel between VNFs, allowing them to pass packets 
encapsulated in UDP ones.

@@

Since our goal shifted into creating a MANO testbed, our prototype doesn't
include PEP. The VNF architecture was shaped following the container
orchestrator we decided to use: Kubernetes.

>>>>

This separation in layers allows to easly manage different identities 
differently: an Internet Service Provider (ISP) could manage different physical
infrastructure and have multiple business emblements dislocated 
along an entire continet for example, but it could decide to have only a single 
centralized business application deployment that manage all the other layers 
resources.

\subsubsection{Network slicing}
The role of a ``network slice'' in a 5G architecture is to specificatly handle 
the Control-plane\todo{Explain what a control plane is?} of a praticular 
service (e.g. smartphones traffic, autonomous driving, massive IoT), deploying 
resources in a manner that assure the required latency, security and 
reliability. While some very peculiar legacy services could require specific 
hardware, the common resources between services could be shared in a 
virtualized way, providing auto-scaling capabilities in services that are under 
heavy network pressure.

@@

The analysis of this topic revealed to be trivial: since internet has many
different protocols that would become infeasible to support all of them at the
same time, packet incapsulation present itself as the only faseable solution:
every packet incoming in the VNFs has already been encapsulated by a generic
packet incapsulator/decapsulator,
\todo{Also I think that the main purpose of UDP encapsulation is not to hide 
the protocol used on the edges but 1) usa a ``quick protocol to exchange data 
among VNFs and 2) we are hiding the path not the protocol itself. As we were 
discussing, we are creating some sort of proxy, so the aim will be the same 
even if we support a plethora of protocols.''} making the whole architecture 
indipendent from the protocol a particolar flux of data. To achieve this, 
several solutions have been studied, and at the end packet incapsulation with 
TCP split (for TCP sessions) have been choosen. The rationale that guided us on 
this choice is described in Chapter~\ref{chap:vnf_ns_impl}. \todo{Update 
reference with the section of the explanation}

@@

Since the requirement for the whole system (MANO+PEP) were too challenging, the 
goal shifted into creating a MANO testbed and a working NFVI, excluding PEP. 
The VNF architecture was shaped following the container orchestrator we decided 
to use. An more detailed architectural implementation can be found at 
Chapter~\ref{chap:archimpl}.

\section{Technologies used}

The development of the ETSI MANO testbed involved the use of several 
tecnhologies already in the market, and in some cases the creation of ad-hoc 
solutions to solve particular issues. Here, a brief listing of the 
well-estabilished technologies used is performed, describing even solutions 
that at the end weren't choosen because they didn't fit with the defined goals.
